---
  output: github_document
---
  
  ```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pace

The goal of *pace* is to 
implement various estimators of Average Causal Effects within principal strata (PACEs) from randomized experiments and observational studies.


## Installation with `devtools`:

```{r, eval = FALSE}
devtools::install_github("shuyang1987/pace")
```

### Main Paper: coming soon

Jiang et al. (2020) Multiply robust estimation of causal effects under principal ignorability. 


### Usage

pace(X,Z,S,Y,family.Y,nboot)

### Arguments

Argument  | 
------------- | -------------
X| is a matrix of pre-treatment covariates without intercept  (n x p).
Z| is a vector of treatment  (n x 1).
S| is a vector of binary intermediate outcome  (n x 1).
Y| is a vector of outcome  ( n x 1).
family.Y| specifies the family for the outcome model.
* |"gaussian": a linear regression model for the continuous outcome.
* |"binomial": a logistic regression model for the binary outcome.
nboot| is the number of bootstrap samples.


### Value

| 
------------- | -------------
Complier|
tau10w| a principal score weighting estimator of tau10
tau10sw| a stabilized weighting estimator of tau10
tau10reg| a regression estimator of tau10 using outcome mean regression and inverse probability of treatment weighting
tau10reg2| a regression estimator of tau10 using outcome mean and principal score regression
tau10aw| a triply robust estimator of tau10
bootstrap variance estimator|ve.tau10w,ve.tau10sw,ve.tau10reg,ve.tau10reg2,ve.tau10aw

| 
------------- | -------------
Never Taker|
tau00w| a principal score weighting estimator of tau00
tau00sw| a stabilized weighting estimator of tau00
tau00reg| a regression estimator of tau00 using outcome mean regression and inverse probability of treatment weighting
tau00reg2| a regression estimator of tau00 using outcome mean and principal score regression
tau00aw| a triply robust estimator of tau00
bootstrap variance estimator|ve.tau00w,ve.tau00sw,ve.tau00reg,ve.tau00reg2,ve.tau00aw

| 
------------- | -------------
Always Taker|
tau11w| a principal score weighting estimator of tau11
tau11sw| a stabilized weighting estimator of tau11
tau11reg| a regression estimator of tau11 using outcome mean regression and inverse probability of treatment weighting
tau11reg2| a regression estimator of tau11 using outcome mean and principal score regression
tau11aw| a triply robust estimator of tau11
bootstrap variance estimator|ve.tau11w,ve.tau11sw,ve.tau11reg,ve.tau11reg2,ve.tau11aw

## Example

Application: An encouragement experiment with non-compliance

```{r Application: An encouragement experiment with non-compliance}

fl = read.table("fludata.txt", header=TRUE, quote="\"")
Z = fl$assign 
S = fl$receive
Y = fl$outcome
X = as.matrix(fl[, -c(1, 2, 3)])
N = length(Z)

out.flu<-pace::pace(X,Z,S,Y,family.Y="binomial",nboot=100)

cname<-c("Est","SE","95%CI","")
rname<-c("w","sw","reg","reg2")
table10<-rbind( 
  c(out.flu$tau10w, sqrt(out.flu$ve.tau10w) , out.flu$tau10w-1.96* sqrt(out.flu$ve.tau10w), out.flu$tau10w+1.96*sqrt(out.flu$ve.tau10w) ),
  c(out.flu$tau10sw, sqrt(out.flu$ve.tau10sw) , out.flu$tau10sw-1.96* sqrt(out.flu$ve.tau10sw), out.flu$tau10sw+1.96*sqrt(out.flu$ve.tau10sw) ),
  c(out.flu$tau10reg, sqrt(out.flu$ve.tau10reg) , out.flu$tau10reg-1.96* sqrt(out.flu$ve.tau10reg), out.flu$tau10reg+1.96*sqrt(out.flu$ve.tau10reg) ),
  c(out.flu$tau10reg2, sqrt(out.flu$ve.tau10reg2) , out.flu$tau10reg2-1.96* sqrt(out.flu$ve.tau10reg2), out.flu$tau10reg2+1.96*sqrt(out.flu$ve.tau10reg2) )
  )
colnames(table10)<-cname
row.names(table10)<-rname

table00<-rbind( 
  c(out.flu$tau00w, sqrt(out.flu$ve.tau00w) , out.flu$tau00w-1.96* sqrt(out.flu$ve.tau00w), out.flu$tau00w+1.96*sqrt(out.flu$ve.tau00w) ),
  c(out.flu$tau00sw, sqrt(out.flu$ve.tau00sw) , out.flu$tau00sw-1.96* sqrt(out.flu$ve.tau00sw), out.flu$tau00sw+1.96*sqrt(out.flu$ve.tau00sw) ),
  c(out.flu$tau00reg, sqrt(out.flu$ve.tau00reg) , out.flu$tau00reg-1.96* sqrt(out.flu$ve.tau00reg), out.flu$tau00reg+1.96*sqrt(out.flu$ve.tau00reg) ),
  c(out.flu$tau00reg2, sqrt(out.flu$ve.tau00reg2) , out.flu$tau00reg2-1.96* sqrt(out.flu$ve.tau00reg2), out.flu$tau00reg2+1.96*sqrt(out.flu$ve.tau00reg2) )
)
colnames(table00)<-cname
row.names(table00)<-rname

table11<-rbind( 
  c(out.flu$tau11w, sqrt(out.flu$ve.tau11w) , out.flu$tau11w-1.96* sqrt(out.flu$ve.tau11w), out.flu$tau11w+1.96*sqrt(out.flu$ve.tau11w) ),
  c(out.flu$tau11sw, sqrt(out.flu$ve.tau11sw) , out.flu$tau11sw-1.96* sqrt(out.flu$ve.tau11sw), out.flu$tau11sw+1.96*sqrt(out.flu$ve.tau11sw) ),
  c(out.flu$tau11reg, sqrt(out.flu$ve.tau11reg) , out.flu$tau11reg-1.96* sqrt(out.flu$ve.tau11reg), out.flu$tau11reg+1.96*sqrt(out.flu$ve.tau11reg) ),
  c(out.flu$tau11reg2, sqrt(out.flu$ve.tau11reg2) , out.flu$tau11reg2-1.96* sqrt(out.flu$ve.tau11reg2), out.flu$tau11reg2+1.96*sqrt(out.flu$ve.tau11reg2) )
)
colnames(table11)<-cname
row.names(table11)<-rname
library(knitr)
print(kable( table10, caption="Results for compliers" ))
print(kable( table00, caption="Results for never takers" ))
print(kable( table11, caption="Results for always takers" ))
```
